\documentclass[10pt]{article}

\usepackage[margin=0.40in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[scaled]{helvet}
\usepackage[none]{hyphenat}
\sloppy

\hypersetup{hidelinks}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

% Section formatting (ATS-safe, single-column, no graphics)
\setlength{\parskip}{0pt}
\newcommand{\ressection}[1]{
  \vspace{0.45em}
  {\large\bfseries #1}\par
  \vspace{0.12em}\hrule\vspace{0.32em}
}

% Compact bullet layout for one-page engineering resumes
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=0pt,
  topsep=1pt,
  parsep=0pt,
  partopsep=0pt
}

\begin{document}

\begin{center}
{\LARGE {\bfseries Santhosh Sankar}} \\
Ann Arbor, MI \enspace $\vert$ \enspace (734) 846-5255 \enspace $\vert$ \enspace
\href{mailto:ssankar@umich.edu}{ssankar@umich.edu} \enspace $\vert$ \enspace
\href{https://www.linkedin.com/in/santhosh-sankar-3241521b8/}{linkedin.com/in/santhosh-sankar-3241521b8} \enspace $\vert$ \enspace
\href{https://github.com/ssankar7775}{github.com/ssankar7775}
\end{center}

\ressection{EDUCATION}

{\bfseries University of Michigan}, Ann Arbor, MI \hfill Jan 2026 -- May 2027 (Expected) \\
Master of Engineering in Space Systems \hfill {\bfseries GPA: 4.0/4.0} \\
Climate and Space Sciences and Engineering Department (CLaSP)

\begin{itemize}
  \item Specialization in Controls and Embedded Systems
  \item Relevant Graduate Coursework: Management of Space Systems, Control System Analysis and Design, Astrodynamics
\end{itemize}

{\bfseries University of Michigan}, Ann Arbor, MI \hfill Aug 2021 -- Aug 2024 \\
Bachelor of Science and Engineering in Aerospace Engineering \\
Department of Aerospace Engineering

\begin{itemize}
  \item Relevant Undergraduate Coursework: Materials Science, Dynamics, Gas Dynamics, Aerodynamics, Propulsion, Structures, Aerospace Control Systems
\end{itemize}

\ressection{EXPERIENCE}

{\bfseries SpaceX}, Graduate Engineer -- Payload Integration, Launch Engineering \hfill Aug 2025 -- Dec 2025 \\
Vandenberg, CA
\begin{itemize}
\item Engineered an additional payload avionics checkout rack, increasing payload processing throughput by 50\% to support increased launch cadence.
\item Developed a simulation environment to validate automated payload avionics checkout sequences, enabling hardware-independent testing and engineer training.
\item Automated payload checkout test plans, reducing required engineering support by 1 hour per launch campaign.
\item Integrated payload avionics hardware supporting Falcon 9 launch processing operations.
\end{itemize}

\textbf{Michigan Experimental Rocketry Organization (MERO)} \hfill Ann Arbor, MI \\
\textit{Avionics Systems Engineer / Responsible Engineer} \hfill Jan 2025 – Present

\begin{itemize}
\item Architecting rocket avionics including flight computer, power distribution, and sensor/actuator interface electronics.
\item Designing custom PCBs for flight computer, power distribution, and sensor/actuator breakout boards supporting guidance, telemetry, and recovery subsystems.
\item Developing embedded firmware for sensor acquisition, actuator control, and telemetry processing.
\item Designing vehicle wiring harnesses and electrical integration for flight hardware.
\item Architecting flight–ground communication software enabling command, telemetry, and ground station monitoring.
\item Implementing sensor fusion algorithms and state estimation using IMU and GPS with planned Extended Kalman Filter implementation.
\end{itemize}

{\bfseries CubeSat Flight Lab -- University of Michigan}, Systems Engineer \hfill Aug 2023 -- Aug 2024 \\
Ann Arbor, MI
\begin{itemize}
  \item Spearheaded high-altitude balloon test campaign for a research CubeSat; authored requirements and integration/test procedures.
  \item Built {\bfseries 6} FlatSat/StratoSat iterations, reducing architecture from 3U 7 kg to 1U 1.2 kg and improving avionics efficiency.
  \item Designed an RP2040 Flight Termination Unit and reduced subsystem mass from {\bfseries 2 kg to 170 g}; validated operation to {\bfseries 35 km altitude}.
  \item Engineered RP2040-based embedded avionics integrating LoRa and GPS for command, tracking, and mission safety.
\end{itemize}

{\bfseries Michigan Aeronautical Science Association (MASA)}, Aerodynamics and Recovery Sub-Team Lead \hfill Apr 2022 -- Apr 2023 \\
Ann Arbor, MI
\begin{itemize}
  \item Led aerodynamic and recovery system development for the collegiate liquid bi-propellant rocket Clementine.
  \item Implemented an MBSE workflow for the Lonely Mission demonstrator, introducing Rolleron-based R\&D to mitigate roll coupling.
  \item Engineered a separation from pyrotechnic to pneumatic deployment, lowering fracture risk in fiberglass airframes.
  \item Optimized fin and fin-can geometry using MATLAB (Mastran), FEA, OpenRocket, and CFD; led fabrication and composite layups.
\end{itemize}


\ressection{TECHNICAL SKILLS}

\textbf{Programming:} Python, C/C++, MATLAB, Simulink \\
\textbf{Embedded Systems:} Microcontrollers (RP2040), Raspberry Pi, embedded firmware, sensor interfaces, telemetry \\
\textbf{Avionics \& Instrumentation:} Oscilloscopes, multimeters, DC supplies, thermal chambers, wind tunnels, spectrum analyzers, Logic Analyzers \\
\textbf{Simulation \& Engineering Tools:} Siemens NX, SolidWorks, Star-CCM+, MATLAB, CFD, FEA, Altium Designer \\
\textbf{Hardware Development:} PCB design, wiring harnesses, composite fabrication, aerospace prototyping \\
\textbf{Project Management:} Requirements, test planning, technical documentation, team leadership
\end{document}